---
title: "Popdemos Pretest"
output:
  html_document:
  df_print: paged
  
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

editor_options: 
  chunk_output_type: console
---
# Introduction
Pretest for POPDEMOS Project that explores the relationship between depictions of fear/anxiety and anger for outgroups, especially right-wing populist groups. 

Analysis run on `r Sys.Date()`. 

# Setup and Data Cleaning 

See code from Alex in popemo_script.R for labeling and recoding. Cannot share data due to privacy concerns. Maybe add a synthetic data set for validation? 

```{r setup}
  library(Rmisc)   #For summarySE function 
  library(tidyverse) 
  library(broom)
  library(beeswarm)

  load("pretest-prepared.rdata")
```

# Descriptives 

### Left-Right Self placement
```{r}
df %>%
  mutate(lr=unclass(links_rechts))%>%
  select(lr)%>%
  summary(.)
```

```{r}
df %>% 
  mutate(lr=unclass(links_rechts))%>%
  select(lr)%>%
  ggplot()+
    aes(x=lr) + 
    geom_histogram(aes(y=..density..), colour="black", fill="white", bins=10)+
    geom_density(alpha=.2, fill="#FF6666") +
    labs(x="Left-Right Self Placement", y="N")+
    theme_bw()
```

Seems roughly normally distributed. Wondering if too many right-wing people in the sample though - since we are looking at outgroups?

  


# Treatment Checks

## Basic Treatment Checks

### To what extent do you share the same opinion as the opinion depicted? 
```{r Share the same opinion}
  df %>%
    summarySE(data=., measurevar = "pt_eins_teilen", group= "treatment", na.rm=T)%>%
    ggplot()+
      aes(x=treatment,y=pt_eins_teilen,ymin=pt_eins_teilen-ci, ymax=pt_eins_teilen+ci)+
      geom_col()+
      geom_errorbar(width=0.4)+
      theme_bw()+
      labs(x="Treatment",y="Share opinion")
```

### To what extent can you understand the opinion depicted? 
```{r understand the opinion}
  df %>%
    summarySE(data=., measurevar = "pt_eins_nachvollziehen", group= "treatment", na.rm=T)%>%
    ggplot()+
      aes(x=treatment,y=pt_eins_nachvollziehen,ymin=pt_eins_nachvollziehen-ci, ymax=pt_eins_nachvollziehen+ci)+
      geom_col()+
      geom_errorbar(width=0.4)+
      theme_bw()+
      labs(x="Treatment",y="Understand opinion")
```





# Prepare Code for Main Analaysis of follow up hypothesis